%===========================
% Resume using AltaCV Class
% Author: Raja Ram Sharma
%===========================

\documentclass[10pt,a4paper,withhyper]{altacv}

% Page geometry and column separation
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% Required for 2-column layout
\usepackage{paracol}

% Use Lato font (pdflatex or xelatex-compatible)
\iftutex
  \setmainfont{Lato}
\else
  \usepackage[default]{lato}
\fi

%-------------- COLOR CONFIG --------------
% Setting all colors to black for minimal and clean look
\definecolor{Black}{HTML}{000000}
\colorlet{heading}{Black}
\colorlet{headingrule}{Black}
\colorlet{accent}{Black}
\colorlet{emphasis}{Black}
\colorlet{body}{Black}

% Customize item and rating markers
\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}
%-------------- BEGIN DOCUMENT --------------
\begin{document}

%---------- HEADER ----------
\name{RAJA RAM SHARMA}
\tagline{}

% Personal information block
\personalinfo{%
  \email{rajaramsharma422@gmail.com}
  \phone{+91-92055 74290}
  \linkedin{ArbitCode}
  \github{ArbitCode}
  \location{New Delhi, India}
}

% Renders the header using above info
\makecvheader

% Smaller font in itemize environments
\AtBeginEnvironment{itemize}{\small}

% Ratio of left:right column
\columnratio{0.6}

% Start the two-column layout
\begin{paracol}{2}

%---------- LEFT COLUMN ----------
\cvsection{Experience}

% IBM job
\cvevent{Software Engineer 2}{IBM, ISDL (India Systems Development Lab)}{Oct 2024 -- Ongoing}{India}
\begin{itemize}
   \item Implementing customer managed policies that can attach to entities (IAM users, IAM groups, and IAM Roles).
    \item Contributed pull requests (C++, Python) to the open-source Ceph organization: \href{https://tinyurl.com/ceph-prs}{View PRs}.
    \item Developed AWS-compatible IAM APIs (e.g., \textit{GetAccountSummary}, \textit{GetCallerIdentity}) to support identity validation and permission introspection for enterprise clients.
    \item Implemented the \textit{RemoveClientIDFromOpenIDConnectProvider} IAM API in RGW to allow dynamic client ID management for OIDC providers.
    \item Implemented integration tests(Python) to validate IAM APIs, improving automated test coverage and upstream compatibility standards.
\end{itemize}

\divider

% OpenText job
\cvevent{Software Engineer}{OpenText}{Nov 2021 -- Oct 2024}{Bangalore, India}
\begin{itemize}
    \item Implemented ZDB and IR techniques features utilize mirror and snapshot technologies of disk-based arrays.
    Create, at high speed, a copy of the data to be backed up and then perform backup operations on the copy, rather than on the original data.
    Restore a backup copy of data, held on the array, to its original location on the array to facilitate high-speed recovery.
    \item Led the development of granular VM backup and recovery functionality used by 50+ enterprise clients, reducing manual restore efforts by 60\% and Implemented multiple REST APIs using Java, JDBC, and PostgreSQL to enable file access for web clients.
    \item Improved Data Protector's VMware, H3C CAS, and PostgreSQL modules, increasing backup coverage by 30\%.
    \item Developed secure, maintainable C++, Java, and Perl code using design patterns and memory-safe practices.
    \item Resolved 50+ bugs and loopholes from customer-reported incidents, improving product stability.
\end{itemize}

\divider

% Internship
\cvevent{Software Engineer Intern}{Midland Credit Management}{Feb 2021 --  Nov 2021}{Gurgaon, India}
\begin{itemize}
    \item Built API-based automation on MuleSoft(iPaaS) to transfer over 10,000 files from SFTP to S3 with near real-time alerts, reducing manual operations by 70\%.
    \item Implemented AWS-based back-end workflows using Lambda, S3, and DynamoDB, resulting in 35\% improvement in data processing speed.
    \item Worked as part of a 10-member agile team; delivered 20+ JIRA-tracked tasks.
\end{itemize}

% Conference section
\cvsection{Conference Talks}
\cvevent{Ceph Days India 2025, Ceph RGW}{User Accounts Feature: Enables AWS-compatible IAM APIs for managing users, roles, and policies.}{2024}{Bangalore, India}

%---------- RIGHT COLUMN ----------
\switchcolumn

% Achievements
\cvsection{Achievements}
\begin{itemize}
    \item Won the Smart India Hackathon — the first time in my college. Worked as part of a 5-member team, where I served as the team lead. We developed an Android application for the Ministry of Education, Government of India.
    \item Secured Rank 3 in the Infosys Digital Make-a-Thon.
\end{itemize}

% Open source
 \cvsection{Open Source}
 \begin{itemize}
     \item Contributor to Ceph (C/C++, Python) — a distributed object storage system.
     \item Implemented IAM APIs, including Customer-Managed Policies and enhanced OIDC support.

 \end{itemize}

% Projects
\cvsection{projects}
\cvevent{Ticket Price Calculator App}{Java, Android Studio}{}{}
\begin{itemize}
    \item Developed an Android application to calculate trip ticket prices using Java, PostgreSQL, and Android Studio.
    \item Implemented the UI and backend for the application to support interaction across multiple screens and handle user input.
\end{itemize}
\cvevent{Transaction Management CLI}{C++, Visual Studio}{}{}
\begin{itemize}
    \item Developed a sample banking system using C++ to simulate common bank account functionalities.
    \item A CLI-based application supporting actions such as account creation, deposit, withdrawal, and admin/user management.
\end{itemize}

% Profiles
\cvsection{profiles}
  \begin{itemize}
  \item \href{https://www.codechef.com/users/rajaram_26}{CodeChef: rajaram\_26}
  \item \href{https://leetcode.com/ArbitCode}{LeetCode: ArbitCode}
  \item \href{https://arbitcode.in}{Portfolio: arbitcode.in}
  \end{itemize}

% Skills
\cvsection{skills}
  \begin{itemize}
    \item C++, Core Java, JavaScript
    \item AWS, MySQL, Git
    \item Design Patterns, Node.js, React.js
  \end{itemize}

% Education
\cvsection{Education}
\cvevent{B.Tech - in Computer Science}{Galgotias University}{2017 -- 2021}{UP, India}

%---------- END OF TWO COLUMNS ----------
\end{paracol}

\end{document}
